### 2020-01-17 paper/sex_selection_spacing-ver3.tex
Add more discussion of fertility results and edit method description

To predict cohort fertility based on the models above, I estimate the probability of 
progression to the next parity for each spell.
I include the spell from marriage to first birth, even those results are not examined 
above because of the problems with capturing the exact timing of marriages for the first 
two rounds of the survey.
The estimated progression probabilities should, however, be less affected by this
problem.

To ensure that the predictions depend solely on sample composition and the estimate, I
use the age at marriage for each woman and predict the likelihood of progressing to
each parity, assuming three years increases in age between each parity.
Hence, for a woman married at age 20, I use age 23 for predicting progression 
to the second birth, 26 for the third, and 29 for the fourth.
[TK Predicted fertility is higher the younger the women and the shorter the assumed spacing?]

@@

The predicted cohort fertility based on the hazard model is consistently higher and
declines faster than the predicted fertility based on the four-parity fertility rate.

The faster decline in predicted fertility based on the hazard model is consistent with
a large bias in the fertility rate measure arising from later marriage, increased use of 
sex selection, and the general increase in birth spacing shown above.

[some TFRs are actually going up!]

[CAVEAT: only first four births, these predicted fertility numbers likely too low,
especially for the lower education groups]

>>>>

To predict cohort fertility based on the hazard models above, I estimate the probability 
of progression to the next parity for each spell.
I include the spell from marriage to first birth, even those results are not examined 
above because of the problems with capturing the exact timing of marriages for the first 
two rounds of the survey.
The estimated progression probabilities should, however, be less affected by this
problem.

To ensure that the predictions depend solely on sample composition and the estimate, I
use the age at marriage for each woman and predict the likelihood of progressing to
each parity, assuming three years increases in age between each parity.
Hence, for a woman married at age 20, I use age 23 for predicting progression 
to the second birth, 26 for the third, and 29 for the fourth.
Decreasing the increases in age between parities leads to slightly higher predicted 
fertility.

@@

The main result is that the predicted cohort fertility based on the hazard model is 
consistently higher and declines faster than the four-parity fertility rate.
The faster decline in predicted fertility based on the hazard model is consistent with
a large bias in the fertility rate measure arising from later marriage, increased use of 
sex selection, and the general increase in birth spacing shown above.

The potential bias in the fertility rate is also evident in the fact that the 
fertility rate is increasing over time for some groups.
For example, urban women with eight to eleven years of education showed 1.84, 1.81, and
1.87 over the last three surveys and the increase from NFHS-3 to NFHS-4 is even larger
for rural women with one to seven years of education.
These increases are likely the result of a stabilization of the age of first birth and
the spacing between births.%
\footnote{
Increases in TFR over time, even in the face of declining fertility is not 
unusual, as shown by Costa Rica \citep{Bongaarts1999}.
}

Despite the decline in the predicted cohort fertility based on the hazard model, these 
are still generally above the generally accepted replacement level of 2.1.
Only for urban women with twelve or more years of education is the predicted cohort
fertility below 2.1, and even then it is still more than 0.3 children higher than the 
fertility rate estimate of 1.5.
Furthermore, because only the first four births are used, the predicted cohort fertility
numbers are likely too low, especially for the lower education groups.
